Results exploration

### 2023-03-17 manuscript/interactive_report.Rmd
fixed interactive document

what is this document...

# Subset

@@

@@

# Create figure
ecaw_plot <- reactive({
  plot(ecaw_plot_data, digits = 1, ordered = FALSE, legend.position = "right") +
  labs(title = "Compared to a typical study using preexisting observational data, a study using an ECAW would be...")
})

# Join the two plots together to make one figure
renderPlot({ typically_plot + ecaw_plot + plot_layout(ncol = 1, nrow = 2) })
```

```{r}
renderPlot({
# Create histogram of the number of observational studies done
filtered_data() %>% 
  # Exclude missing responses
  filter(!is.na(n_studies)) %>% 
  ggplot() +
  aes(x = n_studies) +
  geom_histogram(binwidth = 3) +
  # annotate(geom = "text", x = 200, label = n_studies_missing_text, y = 30) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) +
  labs(
    x = "Number of studies",
    y = "Count",
    title = "Approximately how many studies have you published using a preexisting observational dataset (e.g., the ALSPAC dataset)?"
  ) +
  papaja::theme_apa()
})
```

>>>>

# Settings

@@

# Results from the manuscript

@@

# Create figure
ecaw_plot <- reactive({
  plot(ecaw_plot_data(), digits = 1, ordered = FALSE, legend.position = "right") +
  labs(title = "Compared to a typical study using preexisting observational data, a study using an ECAW would be...")
})

# Join the two plots together to make one figure
renderPlot({ typically_plot() + ecaw_plot() + plot_layout(ncol = 1, nrow = 2) })
```

---

```{r echo=FALSE}
# Used methods figures
method_plot_data <- reactive({
  filtered_data() %>% 
    select(starts_with("method_")) %>% 
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "scale",
    ) %>%
    separate(variable, into = c("name_prefix", "type")) %>% 
    group_by(type) %>% 
    count(scale) %>% 
  ungroup() %>% 
    replace_na(list(scale = "Missing")) %>% 
    mutate(
      scale = factor(scale, levels = c(
          "Never or almost never",
          "Sometimes",
          "About half the time",
          "Most of the time",
          "Always or almost always",
          "Missing",
          "I don't understand the question")
            ),
      type = case_when(
        type == "blind" ~ "Blind the data analyst",
        type == "confirmatory" ~ "Contain confirmatory analysis",
        type == "exploratory" ~ "Contain exploratory analysis",
        type == "preregistered" ~ "Are preregistered",
        type == "script" ~ "Share analysis scripts",
      ),
      type = factor(type, levels = c(
        "Contain exploratory analysis",
        "Contain confirmatory analysis",
        "Blind the data analyst",
        "Share analysis scripts",
        "Are preregistered"
      ))
      ) %>% 
  group_by(type) %>%
  tidyr::complete(scale, fill = list(n = 0)) %>% 
  mutate(
    percentage = n / sum(n)
  ) %>% 
  ungroup()
})

renderPlot({
method_plot_data() %>% 
  # filter(scale %ni% c("Missing", "I don't understand the question")) %>% 
  ggplot() +
  aes(
    x = percentage,
    y = type,
    fill = scale
  ) +
  geom_bar(position = "stack", stat = "identity") +
  scale_x_continuous(
    limits = c(0, 1),
    labels = scales::label_percent()
  ) +
  scale_fill_viridis(option = "A", discrete = TRUE) +
  labs(
    x = "Percentage",
    fill = "Response",
    title = "The studies using preexisting observational data that I am involved in..."
  ) +
  papaja::theme_apa() +
  theme(
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_blank()
  ) 
})
```

---

```{r echo=FALSE}
# Prepare plot data
alspac_plot_data <- reactive({
  filtered_data() %>%
  select(contains("alspac_")) %>% 
  # Transform not wanted response values to NA
  # likert::likert drops NA values silently
  # When var transformed to factor these values would be transformed to NA
  # Automatically but I try to be explicit
  mutate(
    across(
      everything(),
      ~ case_when(
        . %in% c("I don't understand the question", "Unsure") ~ NA_character_,
        TRUE ~ .
      )
    )
  ) %>% 
  mutate(
    across(
      .fns = ~ factor(., levels = c(
          "Strongly disagree",
          "Somewhat disagree",
          "Neither agree nor disagree",
          "Somewhat agree",
          "Strongly agree")
          )
      )
    ) %>% 
  rename(
    `If ALSPAC required that I\nuse an ECAW, I would be less willing to\nuse their data in my research` = alspac_less_willing,
    `If ALSPAC ran a study\non ECAWs, I would opt-in.` = alspac_opt_in,
    `ALSPAC should run\na study on ECAWs.` = alspac_study,
    `I would prefer using\nan ECAW than using typical preregistration` = alspac_prefer_ecaw
  )
})

# Create likert package data not including the missing values
alspac_plot_likert_data <- reactive({likert(alspac_plot_data())})

# Create figure
renderPlot({
  plot(alspac_plot_likert_data(), digits = 1, ordered = TRUE, group.order = names(alspac_plot_data()), text.size = 6) +
  labs(title = "Thinking about a study you may run with ALSPAC data (or one that you have recently run)...") +
  theme(
    title = element_text(size = 14),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 15),
    axis.title.x = element_text(size = 15),
    legend.text = element_text(size = 12),
    legend.title = element_blank()
  )
})
```

# Results from supplementary materials C

```{r echo=FALSE}
renderPlot({
# Create histogram of the number of observational studies done
filtered_data() %>% 
  # Exclude missing responses
  filter(!is.na(n_studies)) %>% 
  ggplot() +
  aes(x = n_studies) +
  geom_histogram(binwidth = 3) +
  # annotate(geom = "text", x = 200, label = n_studies_missing_text, y = 30) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) +
  labs(
    x = "Number of studies",
    y = "Count",
    title = "Approximately how many studies have you published using a preexisting observational dataset (e.g., the ALSPAC dataset)?"
  ) +
  papaja::theme_apa()
})
```

---

```{r echo=FALSE}
# Programming languages table
renderTable({
filtered_data() %>% 
  rename(lang = programming_language) %>% 
  separate_rows(lang, sep = ",") %>% 
  count(lang) %>% 
  replace_na(list(lang = "Missing")) %>% 
  # Removing irrelevant
  filter(lang != "irrelevant") %>% 
  ungroup() %>% 
  mutate(
    `Percentage of respondents` = round(n / sum(n) * 100, 0)
  ) %>% 
  arrange(desc(n)) %>% 
  rename(
    `Programming language` = lang,
    `N` = n
  )
})
```

---

```{r echo=FALSE}
# Concerned figure data preparation
concerned_plot_data <- reactive({
  processed %>% 
  select(concerned) %>% 
  mutate(
    concerned = tolower(concerned),
    concerned = factor(concerned, levels = c(
      "very much less concerned",
      "less concerned",
      "somewhat less concerned",
      "as concerned as a typical researcher in my field",
      "somewhat more concerned",
      "more concerned",
      "very much more concerned"
      )
    )
  ) %>% 
    filter(!is.na(concerned))
})

# Create likert package data not including the missing values
concerned_likert_plot_data <- reactive({likert(concerned_plot_data())})

# Create figure
renderPlot({
  plot(concerned_likert_plot_data(), digits = 1, text.size = 6, group.order = names(concerned_plot_data())) +
  labs(title = "Compared to what you think of as a typical researcher who uses preexisting observational data in your field,\nhow concerned are you with research trustworthiness, bias, rigour, and reproducibility ...") +
  theme(
    title = element_text(size = 14),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 15),
    axis.title.x = element_text(size = 15),
    legend.text = element_text(size = 10),
    legend.title = element_blank()
  )
})
```
